### 2025-06-25 conteudo/results/students.tex
Update students.tex

Groups three, six, and ten created a struct to encapsulate the parameters and mitigate duplication 
when applying the parameterized method. Group three sent the mitigation to the maintainers and 
approved it without significant comments. In contrast, the patch from group ten was rejected by 
the same maintainer who approved the patch from group three. The maintainer justification to reject 
the patch is that group ten refactored code files that has simple context, threfore adding a layer 
of abstraction to remove a duplication deacrease the code readability without clear gains on 
the codebase quality. Figure \ref{fig:group_10_reply} shows the maintainers's feedback for group ten.

>>>>

Groups three, six, and ten created a struct to encapsulate the parameters and mitigate duplication 
when applying the parameterized method. Group three sent the mitigation to the maintainers and 
approved it without significant comments. In contrast, the patch from group ten was rejected by 
the same maintainer who approved the patch from group three. The maintainer justification to reject 
the patch is that group ten refactored code files that has simple context, therefore adding a layer 
of abstraction to remove a duplication deacrease the code readability without clear gains on 
the codebase quality. Figure \ref{fig:group_10_reply} shows the maintainers's feedback for group ten.
